Designing Large-Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-02-16 paper/self_calibration_I.tex
euclid: update paper abstract
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@20264 03a3cea6-2c03-0410-ac9b-9271b1c66c29

\begin{abstract}
In this paper we show that, with a well chosen observing strategy, it is possible to accurately calibrate the large-scale response of instruments used in large-scale imaging surveys with survey science data alone. We create end-to-end simulations of an imaging survey, which produce simulated photometric catalogs from mock observations of a synthetic sky according to a defined survey strategies. These catalog-based simulations include realistic measurement uncertainties and a complex, position-dependent instrument response. We then use a self-calibration technique to recover the relative instrument response by fitting an model that best explains the survey catalog, based on (non-varying) sources that fall on different focal plane positions in multiple observations. By considering four simple survey strategies we find that, with appropriate redundancy built into the survey strategy, it is possible to accurately constrain the large-scale relative photometric response of an imaging instrument, and therefore the relative calibration of all the images and the relative fluxes of all the sources observed. The majority of the remaining post-self-calibration errors are due to the limitations in the basis used to model the relative instrument response. We find that returning the same sources to very different focal plane positions is the key property of any survey strategy designed for accurate retrospective calibration. The results of this work suggest the following advice for those considering the design of large-scale imaging surveys: Do not use a regular tiling of the sky; instead return the same sources to very different focal plane positions.
\end{abstract}

@@

\acknowledgments
\section{Acknowledgments}
DWH was partially supported by NASA (grant XXX), the NSF (grant XXX), and a research fellowship from the Alexander von Humboldt Foundation.

>>>>

\begin{abstract}
In this paper, we investigate under which survey conditions the self-calibration of an instrument response can produce precise photometric catalogs for wide-field imaging surveys, drawing only on the science data themselves. We consider four basic survey strategies and create end-to-end simulations of an imaging survey, which produce simulated photometric catalogs from mock observations of a realistic, synthetic sky. These catalog-based simulations include realistic measurement uncertainties and a complex, position-dependent instrument response. We then use a self-calibration technique to recover the instrument response by fitting an model that best explains the survey catalog, based on the sources that fall on different focal plane positions in separate observations. We demonstrate that with a favorable survey strategy, a complex (but smooth) instrument response can be precisely calibrated using this self-calibration technique. We also find that returning the same sources to very different focal plane positions is the key property of any survey strategy designed for accurate retrospective calibration. The results of this work suggest the following advice for those considering the design of large-scale imaging surveys: Do not use a regular tiling of the sky; instead return the same sources to very different focal plane positions. 
\end{abstract}

@@

\acknowledgments
\section{Acknowledgments}
Rory Holmes was funded by the Deutschen Zentrums f\"ur Luft- und Raumfahrt (DLR) through the grant 50QE1202.

DWH was partially supported by NASA (grant XXX), the NSF (grant XXX), and a research fellowship from the Alexander von Humboldt Foundation.
